Verifying Demonstrations

### 2018-11-30 paper/privacy-analysis.tex
adds a summary sentence at the end of the security evaluation to not have the part of Grace using Alice's private key pop up in the conclusion.

>>>>

Overall, informally, the digital trace needed for verifiability in \CROCUS could
conceivably be used to strengthen a suspicion of
participation. Given A2's (Grace's) inferences from auxiliary information that points
to Alice having participated in a protest, for example pictures at the
event, with face recognition and subsequent identification, IP address
of her home router, etc., then any remaining uncertainty from false
positives could be reduced by learning from data on the ledger and
Alice's smartphone. %This potential difference can thus be considered
                    %the price for verifiability.
For confirmation of that suspicion, Grace would have to get access to
and use Alice's private key.
